What do incoming university students believe about open science practices in

### 2022-03-29 analysis/Manuscript.Rmd
reduce words from Results

We also measured participants' normative beliefs about how researchers actually conduct psychological science. We asked participants, "When you consider all of the psychology studies conducted globally each year, what percentage of them would have the following characteristics?" These practices corresponded approximately to our ten norm–counternorm pairs, with two exceptions (see Table \@ref(tab:normsinpracticeitems)). We excluded the critical thinking norm because it did not refer to externally observable behaviour, and we included another practice out of interest (data sharing on request). Participants indicated their estimate on a slider bar ranging from 0% to 100%.

@@

Estimates were recorded using a slider bar ranging from 0% to 100%. 
A second question asked participants whether they had heard of the replication crisis. Those who had heard of the replication crisis were asked two additional open-ended questions: (1) describe the replication crisis, and (2) name the scientific disciplines most affected by the replication crisis.

@@

In line with our preregistered analysis plan, we calculated the difference in means
between responses to each norm item and its accompanying counternorm, along with 
95% confidence intervals. For this analysis, we removed three cases with missing values. 
Table \@ref(tab:differencebetweennormandcounternorm) displays the means and standard deviations for each norm, counternorm, and the difference values. See Table \@ref(tab:corrbetweennormandcounternorm) in the Supplemental Materials for the correlations between norm and counternorm items.

In general, the students seemed to endorse open science practices: For seven of the ten open science practices, agreement with the norm item was stronger than for the corresponding counternorm. However, the extent to which participants endorsed open science norms varied substantially across different practices. Participants most strongly endorsed norms that researchers should provide sufficient information about studies to permit replicability, be critical of published findings, and avoid p-hacking (means > 4; 4 representing '*agree*'). They also tended to agree that researchers should avoid HARKing, share papers as open access, share open materials, and preregister their studies; the means for these items varied between 3.5 and 4. On the other hand, they tended to disagree with the practice of sharing preprints prior to peer review and, to a lesser extent, with sharing open data.

@@

## Norms in Practice
Participants were also asked to estimate the proportion of psychology studies globally that apply each of ten practices (see Table \@ref(tab:normsinpractice)). For many of these practices, participants’ estimates were near the midpoint of 50%. This said, participants perceived some practices as being applied relatively infrequently: For example, the mean estimate of the prevalence of HARKing, preprint sharing before publication, and open data sharing were all near 30%. See Figure A in Supplemental Materials to see the distribution for each item. Participants perceived the most common practice was providing enough information in written reports to permit replication without asking any questions of the original researchers.

@@

Participants who indicated they had heard of the replication crisis were asked, "What do you think 'the replication crisis' is"? Two independent coders marked the responses as accurate or inaccurate; they agreed on `r perc_agree$value`% of the descriptions and resolved the disagreements through discussion. Of the `r length(df$crisis_text[is.na(df$crisis_text)==FALSE])` participants who answered this question, most (`r sum(crisis_descriptions$accurate =="y")/length(df$crisis_text[is.na(df$crisis_text)==FALSE])*100`%) provided responses consistent with the conventional interpretation of the term (i.e., describing a realisation that some scientific findings cannot be replicated). For example, "Where previously trusted studies have been replicated the results were not able to be replicated". Only `r sum(crisis_descriptions$accurate == "n")` responses indicated a misunderstanding of the term (e.g., "Plagiaris[m]").

>>>>

We also measured participants' normative beliefs about how researchers actually conduct psychological science. We asked participants, "When you consider all of the psychology studies conducted globally each year, what percentage of them would have the following characteristics?" These practices corresponded approximately to our ten norm–counternorm pairs, with two exceptions (see Table \@ref(tab:normsinpracticeitems)). We excluded the critical thinking norm because it did not refer to externally observable behaviour, and we included another practice out of interest (data sharing on request). Participants indicated their estimate on a visual slider from 0% to 100%.

@@

Estimates were recorded using a visual slider from 0% to 100%. 
A second question asked participants whether they had heard of the replication crisis. Those who had heard of the replication crisis were asked two additional open-ended questions: (1) describe the replication crisis, and (2) name the scientific disciplines most affected by the replication crisis.

@@

As preregistered, we calculated the difference in means
between responses to each norm item and its accompanying counternorm (with 
95% confidence intervals). For this analysis, we removed three cases with missing values. 
Table \@ref(tab:differencebetweennormandcounternorm) displays the means and standard deviations for each norm, counternorm, and the difference values. See Table \@ref(tab:corrbetweennormandcounternorm) in the Supplemental Materials for the correlations between norm and counternorm items.

In general, the students seemed to endorse open science practices: For seven of the ten open science practices, agreement with the norm item was stronger than for the corresponding counternorm item. However, participants' endorsement of norms varied substantially across different practices. Participants most strongly endorsed norms that researchers should provide sufficient information about studies to permit replicability, be critical of published findings, and avoid *p*-hacking. They also tended to agree that researchers should avoid HARKing, share papers as open access, share open materials, and preregister their studies. On the other hand, they tended to disagree with the practice of sharing preprints prior to peer review and, to a lesser extent, with sharing open data.

@@

## Norms in Practice
Participants were also asked to estimate the proportion of psychology studies globally that apply each of ten practices (see Table \@ref(tab:normsinpractice)). For many of these practices, participants’ estimates were near the midpoint of 50%. Nonetheless, participants perceived some practices as being applied relatively infrequently: For example, the mean estimate of the prevalence of HARKing, preprint sharing before publication, and open data sharing were all near 30%. See Figure A in Supplemental Materials to see the distribution for each item. Participants perceived that the most common practice was providing enough information in written reports to permit replication without asking questions of the original researchers.

@@

Participants who indicated they had heard of the replication crisis were asked, "What do you think 'the replication crisis' is"? Two independent coders marked the responses as accurate or inaccurate; they agreed on `r perc_agree$value`% of the descriptions and resolved disagreements through discussion. Of the `r length(df$crisis_text[is.na(df$crisis_text)==FALSE])` participants who answered this question, most (`r sum(crisis_descriptions$accurate =="y")/length(df$crisis_text[is.na(df$crisis_text)==FALSE])*100`%) provided responses consistent with the conventional interpretation of the term (i.e., describing a realisation that some scientific findings cannot be replicated). For example, "Where previously trusted studies have been replicated the results were not able to be replicated". Only `r sum(crisis_descriptions$accurate == "n")` responses indicated a misunderstanding of the term (e.g., "Plagiaris[m]").
